Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-05 prop_letter.tex
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating according to the proof in prop_iop.tex...

Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
the space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
consistent with $\bar{\mu}_{2}$ on $\events_{0}$.

@@

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
For every convex IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
\end{thm}

>>>>

Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
the space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it, and the mixed state~$p\proj{0}+\left(1-p\right)\proj{1}$ is
consistent with $\bar{\mu}_{2}$ on $\events_{0}$ for all $p\in\left[0,1\right]$,
because each corresponds to a classical coin with probability~$p$
to get head.

@@

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
\end{thm}
